\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
more mods

This paper is organized as follows. In Section~\ref{sec:background}, we first describe related work in this area. In Section~\ref{sec:survey}, we present details of the online survey including information about the types of trajectories and environments used. Section~\ref{sec:raw_results} presents the results from the survey and analysis, including the trajectory features used for classification and the classification approaches used with the data. In Section~\ref{sec:conclusion}, we conclude with a discussion of how our results could be used to design motion planners that generate more human-acceptable trajectories. 
\begin{figure}
\centering
\begin{tabular}{c|c}
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}} \\
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}} \\
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}} \\
(a) & (b) \\
\end{tabular}
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{2}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{4}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}}
%(a)
%\end{minipage}
%\hfill
%\vline
%\hfill
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{2}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{4}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}}
%(b)
%\end{minipage}
\caption{Example trajectory snapshots for motions that survey participants rated (a) highly and (b) poorly. In (b) the hand of the robot ducks under the table in between the first and middle snapshot.}\label{fig:example_trajectory}
\end{figure}

@@

\section{Survey Results and Analysis}
\label{sec:raw_results}
The survey resulted in at least 20 ratings for each trajectory (so there were a total of 2060 ratings from participants in the survey). In this section, we will first analyze the raw results from the survey (which are interesting in themselves). Subsequently, we will present a set of features that were used to represent individual trajectories. These features will be used in the next section to learn the human-observer ratings for robot trajectories. 
\subsection{Raw Survey Results}
\begin{figure}[h]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
The raw results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of averaged responses for each of the four survey questions across the 103 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. An analysis of the ratings for each trajectory showed that four (averaged) ratings for each individual trajectory were always similar to each other, indicating that users had similar preferences for each trajectory regardless of the individual attributes used to describe the preference for the trajectory (efficient, elegant, smooth, overall). Table~\ref{tab:correlation} shows the Pearson's correlation coefficients corresponding to pairs of attributes. Attributes across individual questions are highly correlated at a statistically significant level of 1\% (with p-values $< 0.01\%$). The 95\% confidence intervals for all the four ratings for each trajectory was less than 1.0. 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
& Efficient & Elegant & Smooth & Overall \\ \hline
Efficient & 1 & 0.96 & 0.91 & 0.98 \\ \hline
Elegant & 0.96 & 1 & 0.96 & 0.98 \\ \hline
Smooth & 0.91 & 0.96 & 1 & 0.96 \\ \hline
Overall & 0.98 & 0.98 & 0.96 & 1 \\ \hline
\end{tabular}
\caption{Correlation between the four attributes in the survey.}
\label{tab:correlation}
\end{table}

@@

\section{Classification}
The survey data provides a great platform to answer the question, ``Can we predict a human-observer preference for a given trajectory?''. Our approach to this question is to let the data drive us towards the answer instead of trying to hand-design a cost function or set of features that offer the best explanation. Towards this end, we chose to learn a classifier based on the available data to help predict the human-observer rating for a new trajectory. The 103 data points (corresponding to the 103 distinct trajectories) were broken up into 3 classes based on average overall ratings:
\begin{itemize}
\item “low” - 11 data points with ratings $\in (1,3]$,
\item “medium”  - 29 data points with ratings $\in (3,5]$,
\item “high” – 63 data points with rating $\in (5,7]$.
\end{itemize}
The data was divided into two samples, a training sample and a test sample, with 1/3rd of each class (overall rating) used to construct the test data sample and the remaining 2/3rd data points within each class used to train the various models. This results in a training set consisting of 68 data points and test set consisting of 35 data points. Table~\ref{tab:test_training} shows how the average overall ratings are distributed across training and test sets.
\begin{table}[h]
\begin{centering}
\begin{tabular}{|c|c|c|c|}
\hline
 & low (1,3] & medium (3,5] & high (5,7] \\ \hline
Training & 7 & 19 & 42 \\ \hline
Test & 4 & 10 & 21 \\ \hline
\end{tabular}
\caption{Distribution between training and test samples.}
\label{tab:test_training}
\end{centering}
\end{table}

>>>>

This paper is organized as follows. In Section~\ref{sec:background}, we first describe related work in this area. In Section~\ref{sec:survey}, we present details of the online survey including information about the types of trajectories and environments used. Section~\ref{sec:raw_results} presents the results from the survey and analysis, including the trajectory features used for classification and Section~\ref{sec:classification} covers the classification approaches used with the data. In Section~\ref{sec:conclusion}, we conclude with a discussion of how our results could be used to design motion planners that generate more human-acceptable trajectories. 
\begin{figure}
\centering
\begin{tabular}{c|c}
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}} \\
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}} \\
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}} \\
(a) & (b) \\
\end{tabular}
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{2}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{4}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}}
%(a)
%\end{minipage}
%\hfill
%\vline
%\hfill
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{2}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{4}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}}
%(b)
%\end{minipage}
\caption{Example trajectory snapshots for motions that survey participants rated (a) highly and (b) poorly. In (b) the hand of the robot ducks under the table in between the first and middle snapshot.}\label{fig:example_trajectory}
\end{figure}

@@

\section{Survey Results and Analysis}
\label{sec:raw_results}
The survey resulted in at least 20 ratings for each trajectory (so there were a total of 2060 ratings from participants in the survey). In this section, we will first analyze the raw results from the survey (which are interesting in themselves). Subsequently, we will present a set of features that were used to represent individual trajectories. These features will be used in the next section to learn the human-observer ratings for robot trajectories. 
\subsection{Raw Survey Results}
\begin{figure}[h]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 4 different attributes for 103 trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Awkward, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
The raw results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of averaged responses for each of the four survey questions across the 103 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. An analysis of the ratings for each trajectory showed that four (averaged) ratings for each individual trajectory were always similar to each other, indicating that users had similar preferences for each trajectory regardless of the individual attributes used to describe the preference for the trajectory (efficient, elegant, smooth, overall). Table~\ref{tab:correlation} shows the Pearson's correlation coefficients corresponding to pairs of attributes. Attributes across individual questions are highly correlated at a statistically significant level of 1\% (with p-values $< 0.01\%$). The 95\% confidence intervals for all the four ratings for each trajectory was less than 1.0. 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
& Efficient & Elegant & Smooth & Overall \\ \hline
Efficient & 1 & 0.96 & 0.91 & 0.98 \\ \hline
Elegant & 0.96 & 1 & 0.96 & 0.98 \\ \hline
Smooth & 0.91 & 0.96 & 1 & 0.96 \\ \hline
Overall & 0.98 & 0.98 & 0.96 & 1 \\ \hline
\end{tabular}
\caption{Correlation between the four attributes in the survey.}
\label{tab:correlation}
\end{table}

@@

\section{Classification}
\label{sec:classification}
The survey data provides a great platform to answer the question, ``Can we predict a human-observer preference for a given trajectory?''. Our approach to this question is to let the data drive us towards the answer instead of trying to hand-design a cost function or set of features that offer the best explanation. Towards this end, we chose to learn a classifier based on the available data to help predict the human-observer rating for a new trajectory. The 103 data points (corresponding to the 103 distinct trajectories) were broken up into 3 classes based on average overall ratings:
\begin{itemize}
\item “low” - 11 data points with ratings $\in (1,3]$,
\item “medium”  - 29 data points with ratings $\in (3,5]$,
\item “high” – 63 data points with rating $\in (5,7]$.
\end{itemize}
The data was divided into two samples, a training sample and a test sample, with 1/3rd of each class (overall rating) used to construct the test data sample and the remaining 2/3rd data points within each class used to train the various models. This results in a training set consisting of 68 data points and test set consisting of 35 data points. Table~\ref{tab:test_training} shows how the average overall ratings are distributed across training and test sets.
\begin{table}[h]
\begin{centering}
\begin{tabular}{|c|c|c|c|}
\hline
 & low (1,3] & medium (3,5] & high (5,7] \\ \hline
Training & 7 & 19 & 42 \\ \hline
Test & 4 & 10 & 21 \\ \hline
\end{tabular}
\caption{Distribution between training and test samples.}
\label{tab:test_training}
\end{centering}
\end{table}
